Model LF

### 2022-09-21 max_dp endogen stød.Rmd
Opdateret pc_ds

```{r}
d_2006q1=create_dummy_ts(start_basic = c(2005, 2), end_basic=c(2020,1),
 dummy_start=c(2006,1), dummy_end = c(2006,1),
 basic_value = 0, dummy_value = 1, frequency = 4)

@@

  unemp = TIMESERIES(c(unemp),   
                     START=c(2005,2),FREQ=4),
  ur = TIMESERIES(c(ur),   
                  START=c(2005,2),FREQ=4),
  uradj = TIMESERIES(c(uradj),   
                     START=c(2005,2),FREQ=4),
  lf = TIMESERIES(c(LF),   
                  START=c(2005,2),FREQ=4),
  pc_ds = TIMESERIES(c(pc_ds),   
                     START=c(2005,2),FREQ=4),
  pc = TIMESERIES(c(pc),   
                  START=c(2005,2),FREQ=4),
  mkp = TIMESERIES(c(mkp),   
                   START=c(2005,2),FREQ=4),

@@

@@

@@

nben_h_01 = Shock_1$simulation$nben_h
```

@@

plot(nben_h_01, col= "red"); lines(nben_h_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

>>>>

d_2011q2=create_dummy_ts(start_basic = c(2005, 2), end_basic=c(2020,1),
 dummy_start=c(2011,2), dummy_end = c(2011,2),
 basic_value = 0, dummy_value = 1, frequency = 4)

d_2013q1=create_dummy_ts(start_basic = c(2005, 2), end_basic=c(2020,1),
 dummy_start=c(2013,1), dummy_end = c(2013,1),
 basic_value = 0, dummy_value = 1, frequency = 4)

d_2017q3=create_dummy_ts(start_basic = c(2005, 2), end_basic=c(2020,1),
 dummy_start=c(2017,3), dummy_end = c(2017,3),
 basic_value = 0, dummy_value = 1, frequency = 4)

d_2006q1=create_dummy_ts(start_basic = c(2005, 2), end_basic=c(2020,1),
 dummy_start=c(2006,1), dummy_end = c(2006,1),
 basic_value = 0, dummy_value = 1, frequency = 4)

@@

  unemp = TIMESERIES(c(unemp),   
                     START=c(2005,2),FREQ=4),
  ur = TIMESERIES(c(ur),   
                  START=c(2005,2),FREQ=4),
  uradj = TIMESERIES(c(uradj),   
                     START=c(2005,2),FREQ=4),
  lf = TIMESERIES(c(LF),   
                  START=c(2005,2),FREQ=4),
  pc = TIMESERIES(c(pc),   
                  START=c(2005,2),FREQ=4),
  mkp = TIMESERIES(c(mkp),   
                   START=c(2005,2),FREQ=4),

@@

  d_2011q2 = TIMESERIES(c(d_2011q2),   
                        START=c(2005,2),FREQ=4),

  d_2013q1 = TIMESERIES(c(d_2013q1),   
                        START=c(2005,2),FREQ=4),
  d_2017q3 = TIMESERIES(c(d_2017q3),   
                        START=c(2005,2),FREQ=4),

@@

plot(nben_h_rest_00, col= "green"); lines(nben_h_rest_obs, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

@@

nben_h_01 = Shock_1$simulation$nben_h

nben_h_rest_01 = Shock_1$simulation$nben_h_rest
```

@@

plot(nben_h_01, col= "red"); lines(nben_h_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
